---
title: "Checks on New Data"
author: "James Hunter"
date: "August 12, 2015"
output: pdf_document
---

Run basic checks on 1st record in new data sent by USP
```{r}
x
x %in% pacientes$amostraid
load(file = "mut.RData")
x %in% mutations$id
xmuts <- which(mutations$id == x)
mutations[xmuts,]
```
 The csv file is represented correctly in the mutations database
 
 The next step is to organize all the id numbers from the csv files from USP and check against the records in `patients` and `mutations`.
 
 
```{r filelist}
dir <- "out_w_fasta"  # location of USP data
filelist <- list.files(path = dir, pattern = "csv")
numfiles = length(filelist)
```

Make vector of `mutations$id` and of `patients$amostraid`
```{r vectors}
mut_id <- mutations$id
pac_id <- pacientes$amostraid
```

Make list of all the amostraid's from the USP files using a loop

```{r getamostraids}
# passar por todos os arquivos, ler o conteúdo de cada mutação e copiar para data frame # das mutações

# set up a blank character vector for USP id's
uspID <- vector(mode = "character", length = numfiles)
# date <- vector(mode = "character", length = numfiles) leave out for now

for (i in 1:numfiles) {
   fullfile <- paste(dir, "/", filelist[i], sep = "")
   temp <- NULL
# ler o arquivo na memoria como variável temp
   try(temp <- read.csv(fullfile, header = FALSE, 
                        stringsAsFactors = FALSE), silent = TRUE)
   if (is.null(temp)) badcsvformat <- c(badcsvformat, filelist[i])
      else
# extract the first cell and row info [1,1] and add to vector of USPids
      uspID[i] <- substr(temp[1,1], 1, 9)
}
# get rid of the empty ID's ("")p
uspID <- uspID[uspID != ""]
```

Get vector with hits in patient database and in mutations database
```{r hits}
hits_mut <- which(uspID %in% mutations$id)
hits_pac <- which(uspID %in% pacientes$amostraid)

```


